The Art of Robotics:\\\vspace{0.2em}\huge{Toward a Holistic Approach}

### 2018-07-31 ms-thesis-slides.tex
almost there...

		\begin{frame}
			\frametitle{How I Ended Up Here (Some Context) II}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=center] (ri-logo) at (current page.center) {\includegraphics[width=30mm]{assets/ri-logo.eps}};
				\node[minimum width=2cm, below=5mm of ri-logo] {``Time to become a robotics master...''};
			\end{tikzpicture}
		\end{frame}

		\begin{frame}
			\frametitle{How I Ended Up Here (Some Context) III}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
				\fontsize{12}{10}
				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
				\node[minimum width=2cm, right=3mm of me] {``Legged locomotion is cool...''};
			\end{tikzpicture}
		\end{frame}

		\begin{frame}
			\frametitle{How I Ended Up Here (Some Context) IV}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
				\fontsize{12}{10}
				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
				\node[minimum width=2cm, right=3mm of me] {\color{gray}``Legged locomotion is cool...''};
				\node[anchor=north east] (hartmut) at ($(current page.north east)+(-5mm,-15mm)$) {\includegraphics[width=2cm]{media/hartmut.jpg}};
				\node[anchor=north east] (travers) at ($(current page.north east)+(-28mm,-15mm)$) {\includegraphics[width=2cm]{media/travers.jpg}};
				\node[anchor=north east] (koushil) at ($(current page.north east)+(-51mm,-15mm)$) {\includegraphics[width=2cm]{media/koushil.jpg}};
				\node[anchor=east, minimum width=2cm, left=3mm of koushil] {``Great! Here's absolutely no funding.''};
			\end{tikzpicture}
		\end{frame}

		\begin{frame}
			\frametitle{How I Ended Up Here (Some Context) V}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
				\fontsize{12}{10}
				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
				\node[minimum width=2cm, right=3mm of me] {``Umm...''};
				\node[anchor=north east] (hartmut) at ($(current page.north east)+(-5mm,-15mm)$) {\includegraphics[width=2cm]{media/hartmut.jpg}};
				\node[anchor=north east] (travers) at ($(current page.north east)+(-28mm,-15mm)$) {\includegraphics[width=2cm]{media/travers.jpg}};
				\node[anchor=north east] (koushil) at ($(current page.north east)+(-51mm,-15mm)$) {\includegraphics[width=2cm]{media/koushil.jpg}};
				\node[anchor=east, minimum width=2cm, left=3mm of koushil] {\color{gray}``Great! Here's absolutely no funding.''};
			\end{tikzpicture}
		\end{frame}

		\begin{frame}
			\frametitle{How I Ended Up Here (Some Context) VI}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
				\fontsize{12}{10}
				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
				\node[minimum width=2cm, right=3mm of me] {\color{gray}``Umm...''};
				\node[anchor=north east] (ross) at ($(current page.north east)+(-5mm,-15mm)$) {\includegraphics[width=2cm]{media/ross.jpg}};
				\node[anchor=east, minimum width=2cm, left=3mm of ross] {``Wait! Go talk to Matt Mason!''};
			\end{tikzpicture}
		\end{frame}

		\begin{frame}
			\frametitle{How I Ended Up Here (Some Context) VII}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
				\fontsize{12}{10}
				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
				\node[minimum width=2cm, right=3mm of me] {``(skeptical) Okay...''};
				\node[anchor=north east] (ross) at ($(current page.north east)+(-5mm,-15mm)$) {\includegraphics[width=2cm]{media/ross.jpg}};
				\node[anchor=east, minimum width=2cm, left=3mm of ross] {\color{gray}``Wait! Go talk to Matt Mason!''};
			\end{tikzpicture}
		\end{frame}

		\begin{frame}
			\frametitle{How I Ended Up Here (Some Context) VIII}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
				\fontsize{12}{15}
				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
				\node[minimum width=2cm, right=3mm of me] {\color{gray}``(skeptical) Okay...''};
				\node[anchor=north east] (matt) at ($(current page.north east)+(-5mm,-15mm)$) {\includegraphics[width=2cm]{media/mason.jpg}};
				\node[anchor=east, text width=5cm, left=3mm of matt, align=right] {``Manipulation is awesome! \\And I have money! \\And I don't micromanage!''};
			\end{tikzpicture}
		\end{frame}

		\begin{frame}
			\frametitle{How I Ended Up Here (Some Context) IX}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
				\fontsize{12}{15}
				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
				\node[minimum width=2cm, right=3mm of me] {``(excited) Works for me!''};
				\node[anchor=north east] (matt) at ($(current page.north east)+(-5mm,-15mm)$) {\includegraphics[width=2cm]{media/mason.jpg}};
				\node[anchor=east, text width=5cm, left=3mm of matt, align=right] {\color{gray}``Manipulation is awesome! \\And I have money! \\And I don't micromanage!''};
			\end{tikzpicture}
		\end{frame}

		\begin{frame}
			\frametitle{How I Ended Up Here (Some Context) X}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
				\fontsize{12}{15}
				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
				\node[minimum width=2cm, right=3mm of me] {\color{gray}``(excited) Works for me!''};
				\node[anchor=north east] (matt) at ($(current page.north east)+(-5mm,-15mm)$) {\includegraphics[width=2cm]{media/mason.jpg}};
				\node[anchor=east, minimum width=2cm, left=3mm of matt, align=right] {``Fantastic, go forth and prosper!''};
			\end{tikzpicture}
		\end{frame}

		\begin{frame}
			\frametitle{How I Ended Up Here (Some Context) XI}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
				\fontsize{12}{15}
				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
				\node[text width=8cm, right=3mm of me, align=left] {``I've been meaning to read Hogan's famous \emph{Impedance Control}~\autocite{hogan1985impedance} paper, I guess I'll start there...''};
			\end{tikzpicture}
		\end{frame}

		\begin{frame}
			\frametitle{How I Ended Up Here (Some Context) XII}
			\begin{tikzpicture}[overlay, remember picture]
				\fontsize{18}{15}
				\node[anchor=center, minimum width=2cm] at (current page.center) {\dots~Two Years Later \dots};
			\end{tikzpicture}
		\end{frame}

@@

		\begin{frame}

		\begin{frame}
			\frametitle{Problem 2: Locomotion and Manipulation, Segregated}
			\begin{itemize}
				\item Locomotion and manipulation are studied separately in robotics\pause
					\begin{itemize}
						\item \dots~and biomechanics, for that matter
						\item Seems quite natural at first, we all talk about the two as separate specializations in robotics
					\end{itemize}\pause
				\item Eventually, the notion of \emph{``duality''} comes up\dots
				\begin{itemize}\pause
					\item Locomotion and manipulation sometimes overlap
						\begin{itemize}
							\item Pai et al.'s \emph{Platonic Beasts} \autocite{pai1994platonic}
							\item Mason et al.'s \emph{Mobipulator} \autocite{MasonMobileManipulator1999} \autocite{MasonDesktopMobileManipulators2000}
							\item Also, literally everywhere in biology
						\end{itemize}
					\item Perhaps it just comes down to a change of reference?
						\begin{itemize}
							\item What pushes off of what?
							\item Locomotion is ``self-manipulation'', e.g. Aaron Johnson's PhD thesis \autocite{johnson2014self} and related works \autocite{johnson2012standing}\autocite{johnson2016hybrid}
						\end{itemize}
				\end{itemize}
			\end{itemize}
		\end{frame}

		\begin{frame}
			\frametitle{Problem 2: Locomotion and Manipulation, United}
			\begin{itemize}
				\item Taking the ``self-manipulation'' perspective
			\end{itemize}
		\end{frame}

@@

	\section{A Unifying Framework}
		\begin{frame}
			\frametitle{The Port-Hamiltonian Framework}
			\begin{itemize}
				\item Port-based Analysis
				\item Hamiltonian Dynamics
					\begin{itemize}
						\item 
					\end{itemize}
				\item
			\end{itemize}
		\end{frame}

		\begin{frame}
			\frametitle{Bond Graphs}

@@

	\nocite{*}
	\begin{frame}[allowframebreaks]
		\frametitle{Bibliography}
		\printbibliography[heading=none]
	\end{frame}

>>>>

		\begin{frame}
			\addtocounter{framenumber}{-1}
			\frametitle{How I Ended Up Here (Some Context) II}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=center] (ri-logo) at (current page.center) {\includegraphics[width=30mm]{assets/ri-logo.eps}};
				\node[minimum width=2cm, below=5mm of ri-logo] {``Time to become a robotics master...''};
			\end{tikzpicture}
		\end{frame}

		\begin{frame}
			\addtocounter{framenumber}{-1}
			\frametitle{How I Ended Up Here (Some Context) III}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
				\fontsize{12}{10}
				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
				\node[minimum width=2cm, right=3mm of me] {``Legged locomotion is cool...''};
			\end{tikzpicture}
		\end{frame}

		\begin{frame}
			\addtocounter{framenumber}{-1}
			\frametitle{How I Ended Up Here (Some Context) IV}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
				\fontsize{12}{10}
				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
				\node[minimum width=2cm, right=3mm of me] {\color{gray}``Legged locomotion is cool...''};
				\node[anchor=north east] (hartmut) at ($(current page.north east)+(-5mm,-15mm)$) {\includegraphics[width=2cm]{media/hartmut.jpg}};
				\node[anchor=north east] (travers) at ($(current page.north east)+(-28mm,-15mm)$) {\includegraphics[width=2cm]{media/travers.jpg}};
				\node[anchor=north east] (koushil) at ($(current page.north east)+(-51mm,-15mm)$) {\includegraphics[width=2cm]{media/koushil.jpg}};
				\node[anchor=east, minimum width=2cm, left=3mm of koushil] {``Great! Here's absolutely no funding.''};
			\end{tikzpicture}
		\end{frame}

		\begin{frame}
			\addtocounter{framenumber}{-1}
			\frametitle{How I Ended Up Here (Some Context) V}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
				\fontsize{12}{10}
				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
				\node[minimum width=2cm, right=3mm of me] {``Umm...''};
				\node[anchor=north east] (hartmut) at ($(current page.north east)+(-5mm,-15mm)$) {\includegraphics[width=2cm]{media/hartmut.jpg}};
				\node[anchor=north east] (travers) at ($(current page.north east)+(-28mm,-15mm)$) {\includegraphics[width=2cm]{media/travers.jpg}};
				\node[anchor=north east] (koushil) at ($(current page.north east)+(-51mm,-15mm)$) {\includegraphics[width=2cm]{media/koushil.jpg}};
				\node[anchor=east, minimum width=2cm, left=3mm of koushil] {\color{gray}``Great! Here's absolutely no funding.''};
			\end{tikzpicture}
		\end{frame}

		\begin{frame}
			\addtocounter{framenumber}{-1}
			\frametitle{How I Ended Up Here (Some Context) VI}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
				\fontsize{12}{10}
				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
				\node[minimum width=2cm, right=3mm of me] {\color{gray}``Umm...''};
				\node[anchor=north east] (ross) at ($(current page.north east)+(-5mm,-15mm)$) {\includegraphics[width=2cm]{media/ross.jpg}};
				\node[anchor=east, minimum width=2cm, left=3mm of ross] {``Wait! Go talk to Matt Mason!''};
			\end{tikzpicture}
		\end{frame}

		\begin{frame}
			\addtocounter{framenumber}{-1}
			\frametitle{How I Ended Up Here (Some Context) VII}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
				\fontsize{12}{10}
				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
				\node[minimum width=2cm, right=3mm of me] {``(skeptical) Okay...''};
				\node[anchor=north east] (ross) at ($(current page.north east)+(-5mm,-15mm)$) {\includegraphics[width=2cm]{media/ross.jpg}};
				\node[anchor=east, minimum width=2cm, left=3mm of ross] {\color{gray}``Wait! Go talk to Matt Mason!''};
			\end{tikzpicture}
		\end{frame}

		\begin{frame}
			\addtocounter{framenumber}{-1}
			\frametitle{How I Ended Up Here (Some Context) VIII}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
				\fontsize{12}{15}
				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
				\node[minimum width=2cm, right=3mm of me] {\color{gray}``(skeptical) Okay...''};
				\node[anchor=north east] (matt) at ($(current page.north east)+(-5mm,-15mm)$) {\includegraphics[width=2cm]{media/mason.jpg}};
				\node[anchor=east, text width=5cm, left=3mm of matt, align=right] {``Manipulation is awesome! \\And I have money! \\And I don't micromanage!''};
			\end{tikzpicture}
		\end{frame}

		\begin{frame}
			\addtocounter{framenumber}{-1}
			\frametitle{How I Ended Up Here (Some Context) IX}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
				\fontsize{12}{15}
				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
				\node[minimum width=2cm, right=3mm of me] {``(excited) Works for me!''};
				\node[anchor=north east] (matt) at ($(current page.north east)+(-5mm,-15mm)$) {\includegraphics[width=2cm]{media/mason.jpg}};
				\node[anchor=east, text width=5cm, left=3mm of matt, align=right] {\color{gray}``Manipulation is awesome! \\And I have money! \\And I don't micromanage!''};
			\end{tikzpicture}
		\end{frame}

		\begin{frame}
			\addtocounter{framenumber}{-1}
			\frametitle{How I Ended Up Here (Some Context) X}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
				\fontsize{12}{15}
				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
				\node[minimum width=2cm, right=3mm of me] {\color{gray}``(excited) Works for me!''};
				\node[anchor=north east] (matt) at ($(current page.north east)+(-5mm,-15mm)$) {\includegraphics[width=2cm]{media/mason.jpg}};
				\node[anchor=east, minimum width=2cm, left=3mm of matt, align=right] {``Fantastic, go forth and prosper!''};
			\end{tikzpicture}
		\end{frame}

		\begin{frame}
			\addtocounter{framenumber}{-1}
			\frametitle{How I Ended Up Here (Some Context) XI}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
				\fontsize{12}{15}
				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
				\node[text width=8cm, right=3mm of me, align=left] {``I've been meaning to read Hogan's famous \emph{Impedance Control}~\autocite{hogan1985impedance} paper, I guess I'll start there...''};
			\end{tikzpicture}
		\end{frame}

		\begin{frame}
			\addtocounter{framenumber}{-1}
			\frametitle{How I Ended Up Here (Some Context) XII}
			\begin{tikzpicture}[overlay, remember picture]
				\fontsize{18}{15}
				\node[anchor=center, minimum width=2cm] at (current page.center) {\dots~Two Years Later \dots};
			\end{tikzpicture}
		\end{frame}

@@

		\begin{frame}
			\frametitle{Problem 2: What is Manipulation?}
			\begin{itemize}
				\item To be honest, I had a very shallow understanding of manipulation until I met Matt \pause
					\begin{itemize}
						\item I imagined it was just factory robot stuff \pause
						\item It took some reflection to appreciate the depth of ``manipulation''
					\end{itemize}
			\end{itemize}
		\end{frame}

		\begin{frame}
			\frametitle{Problem 2: What is Manipulation?}
			\begin{tikzpicture}[overlay, remember picture]
				\fontsize{15}{12}
				\node[anchor=center, text width=0.8\textwidth,align=center] (manip-def) at ($(current page.center)+(0,-3mm)$) {``Manipulation refers to an agent’s control of its environment through selective contact.''};
				\small
				\node[anchor=south east, align=right] at ($(current page.south east)+(-1cm,1cm)$) {--- \emph{Matt Mason}, ``Toward Robotic Manipulation'' \autocite{Mason2018}};
			\end{tikzpicture}
		\end{frame}

		\begin{frame}
			\frametitle{Problem 3: Locomotion and Manipulation, Segregated}
			\begin{itemize}
				\item Locomotion and manipulation are studied separately in robotics\pause
					\begin{itemize}
						\item \dots~and biomechanics, for that matter
						\item Seems quite natural at first, we all talk about the two as separate specializations in robotics
					\end{itemize}\pause
				\item Eventually, the notion of \emph{``duality''} comes up\dots
				\begin{itemize}\pause
					\item Locomotion and manipulation sometimes overlap
						\begin{itemize}
							\item Pai et al.'s \emph{Platonic Beasts} \autocite{pai1994platonic}
							\item Mason et al.'s \emph{Mobipulator} \autocite{MasonMobileManipulator1999} \autocite{MasonDesktopMobileManipulators2000}
							\item Also, literally everywhere in biology
						\end{itemize}
					\item Perhaps it just comes down to a change of reference?
						\begin{itemize}
							\item Just a matter of ``what pushes off of what?''
							\item Locomotion is ``self-manipulation'', e.g. Aaron Johnson's PhD thesis \autocite{johnson2014self} and related works \autocite{johnson2012standing}\autocite{johnson2016hybrid}
						\end{itemize}
				\end{itemize}
			\end{itemize}
		\end{frame}

		\begin{frame}
			\frametitle{Problem 3: Locomotion and Manipulation, United}
			\vspace{-6em}
			\begin{itemize}
				\item The ``self-manipulation'' view of locomotion is consistent with our definition of ``manipulation'':
					\begin{itemize}
						\item An agent may control its environment through selective contact (i.e. ``manipulation'') by moving about in it (i.e. ``locomotion''). \footnotemark
					\end{itemize}
			\end{itemize}
			\footnotetext{It helps to take on an egocentric point of view to visualize this.}
			\pause
			\begin{tikzpicture}[overlay, remember picture]
				\fontsize{15}{12}
				\node[anchor=center,text width=0.8\textwidth,align=center] (loco-manip) at ($(current page.center)+(0,-10mm)$) {So locomotion is just a subset of manipulation!};
			\end{tikzpicture}
		\end{frame}

		\begin{frame}
			\frametitle{Problem 3: Locomotion and Manipulation, United}
			\begin{itemize}
				\item Not a terribly practical insight\dots \pause~but thinking back to \emph{Problem 1}\dots
			\end{itemize}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=center,text width=0.8\textwidth,align=center] (loco-manip) at ($(current page.center)+(0,-10mm)$) {So locomotion is just a subset of manipulation!};
			\end{tikzpicture}
		\end{frame}

@@

	\section{A Unifying Framework}
		\begin{frame}
			\frametitle{Port-Hamiltonian Systems Theory}
			\begin{itemize}
				\item Port-based Analysis
					\begin{itemize}
						\item Inherits the bond-graph notion of power ports
						\item Treats systems in terms of power flow between components
						\item Each bond represents the conjugate pair of an effort and flow
					\end{itemize}\pause
				\item Hamiltonian Dynamics
					\begin{itemize}
						\item Provides a fully geometric (intrinsic, coordinate free) description of system dynamics
						\item Equivalent to (and convertible from/to) Lagrangian formulation
							\begin{itemize}
								\item Whereas Lagrangian dynamics derives solely from variation principles, the Hamiltonian formulation 
								\item Riemannian geometry of Lagrangian dynamics replaced with symplectic geometry, in which fundamental invariants are preserved.
								\item Configuration space of Lagrangian dynamics replaced with state space
							\end{itemize}
					\end{itemize}
			\end{itemize}
		\end{frame}

		\begin{frame}
			\frametitle{Bond-Graphs}

@@

	\section{Bibliography}
	\nocite{*}
	\begin{frame}[allowframebreaks]
		\frametitle{Bibliography}
		\printbibliography[heading=none]
	\end{frame}
